### 2021-10-07 paper/pldi22/related.tex
Added related work with references

\begin{itemize}
  \item Semantics of programming languages: A tool-oriented approach~\cite{lda}
  \item LISA: An interactive environment for programming language
    development~\cite{lisa}
  \item When and how to develop domain-specific languages~\cite{dsl-survey}
  \item Incremental programming language development~\cite{ipld}
\end{itemize}

>>>>

\begin{itemize}
  \item JavaScript specificaiton: ECMAScript (ES12, 2021)~\cite{es12}
  \item JavaScript tests: Test262~\cite{test262}
  \item JavaScript tools: engines~\cite{v8, jscore, chakra, spidermonkey},
    static analyzers~\cite{safe, safe2, tajs, wala, jsai},
    debugger~\cite{jsexplain}, verification tools~\cite{javert, javert2,
    ad-safety, javanni}, symbolic execution~\cite{symbolic-js, sym-js, expo-se},
    concolic testing~\cite{jalangi, type-conc-test}.
  \item Language Design Assistant (LDA)~\cite{lda, lisa, ipld, asf-sdf,
    meta-env}
  \item Domain Specific Language (DSL)~\cite{dsl-survey, dsl-survey2}
  \item Live Programming~\cite{omnicode, situ-vis, proj-box}
  \item JISET family: JISET~\cite{jiset}, JEST~\cite{jest}, JSTAR~\cite{jstar}.
  \item Partial Evaluation~\cite{peval, peval-survey}
\end{itemize}
